Decentralised Authoring, Annotations and Notifications for a Read-Write Web with dokieli

### 2017-04-07 index.tex
deleted unnecessary word

\par \url{https://linkedresearch.org/} uses dokieli in its templates on the site as well as workshop proposals and call for contributions.
                                    \url{http://csarven.ca/} uses dokieli in full, where some articles (like this article) offer pointers to a public annotation service in which users may wish to use for their annotations. Articles also dynamically embed annotations from personal storage spaces.

>>>>

\par \url{https://linkedresearch.org/} uses dokieli in its templates on the site as well as workshop proposals and call for contributions.
                                    \url{http://csarven.ca/} uses dokieli in full, where some articles (like this article) offer pointers to a public annotation service which users may wish to use for their annotations. Articles also dynamically embed annotations from personal storage spaces.
